The Linux Programming Interfaces

### 2019-09-10 CS/note_TLPI.tex
paper

\documentclass{article}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{verbatim}
\usepackage{xeCJK}
\usepackage{hyperref}
\usepackage{listings}
\lstset{
 columns=fixed,       
 numbers=left,                                        % 在左侧显示行号
 numberstyle=\tiny\color{gray},                       % 设定行号格式
 frame=single,                                          % 不显示背景边框
 keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
 numberstyle=\footnotesize\color{darkgray},           
 commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
 stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
 showstringspaces=false,                              % 不显示字符串中的空格
 language=c++,                                        % 设置语言
}
\newcommand{\paper}[2]{\hyperlink{./papers/#1.pdf.#2}{(P#2)}}
\newcommand{\book}[1]{\href[page=#1]{./books/TLPI.pdf}{(P#1)}}

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{unicode-math}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\usepackage{graphicx}
\graphicspath{{./images/}}

\usepackage{pdfpages}
\usepackage{verbatim}
\usepackage{xeCJK}
\usepackage{hyperref}
%\usepackage{apacite}
\usepackage{natbib}
\usepackage{grffile}
\usepackage{listings}
\lstset{
 columns=fixed,       
 numbers=left,                                        % 在左侧显示行号
 numberstyle=\tiny\color{gray},                       % 设定行号格式
 frame=single,                                          % 不显示背景边框
 keywordstyle=\color[RGB]{40,40,255},                 % 设定关键字颜色
 numberstyle=\footnotesize\color{darkgray},           
 commentstyle=\it\color[RGB]{0,96,96},                % 设置代码注释的格式
 stringstyle=\rmfamily\slshape\color[RGB]{128,0,0},   % 设置字符串格式
 showstringspaces=true,                              % 显示字符串中的空格
 language=c++,                                        % 设置语言
}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
%--------Commands for local pdf reference------%
\newcommand{\citeint}[2]{\cite{#1}\hyperlink{./references/#1.pdf.#2}{(P#2)}}
\newcommand{\citeext}[2]{\href[page=#2]{../references/#1.pdf}{(P#2)}}
\newcommand{\citeinclude}[1]{\includepdf[link=true,pages=-,fitpaper=true]{./references/#1.pdf}}
\newcommand{\book}[1]{\citeext{TLPI}{#1}}
%--------Commands/Operators for math------%
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
%--------Environments for math------------%
\newcounter{topic}[subsection]
\newenvironment{defi}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
   \noindent \textbf{Definition~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
\newenvironment{theo}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
   \noindent \textbf{Theorem~\thesubsection.\thetopic~} \rmfamily }{\medskip}
\newenvironment{coro}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
   \noindent \textbf{Corollary~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
\newenvironment{lemm}{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
   \noindent \textbf{Lemma~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
\newenvironment{exam}[1]{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
   \noindent \textbf{Example~\thesubsection.\thetopic~} \rmfamily }{ \medskip}

\newenvironment{rema}[1]{\refstepcounter{topic}\label{\thesubsection.\thetopic}\par\medskip
   \noindent \textbf{Remark~\thesubsection.\thetopic~} \rmfamily }{ \medskip}
\newenvironment{prof}{\par\medskip \noindent \textit{Proof.}~\rmfamily}{\medskip}

@@

\setcounter{section}{5}
\section{Processes}
\subsection{Processes and Programs}
\href{https://en.wikipedia.org/wiki/Executable\_and\_Linkable\_Format}{Executable and Linking Format}
\subsection{Process ID and Parent Process ID}
\subsection{Memory Layout of a Process}
\textit{segments}:\\
The memory allocated to each process. Including:
\begin{itemize}
        \item \textit{text segment}: Machine-language instructions. Read-only, shared. \\
        \item \textit{Initialized data segment}: global and static variables explicitly initialized. \\
        \item \textit{Uninitialized data segment}. \\
        \item \textit{Stack}. One stack frame for each current called function. \\
        \item \textit{Heap}: dynamically allocated data.
\end{itemize}
\subsection{Virtual Memory Management}
Figure: Typical memory layout of a process.\book{163}\\
\textcolor{green}{\textit{pages}}:\\
A virtual memory scheme splits the memory used by each program into small fixed-size units called pages. \\
\textit{page table}: \book{164} \\
Processes can use \textit{shmget()} and \textit{mmap()} to explicitly request sharing of memory regions with other processes, for the purpose of \textcolor{red}{interprocess communication}. \\

\subsection{The Stack and Stack Frames}
\href{http://www.cs.uwm.edu/classes/cs315/Bacon/Lecture/HTML/ch10s07.html}{See this lecture} \\
